%\begin{document}
\section{Report organisation}
This report is organised as follows:
\begin{itemize}
%\item In Chapter~\ref{ch:state-art}, the state of the art of remote controlled
%vehicles is presented.
\item In Chapter~\ref{ch:theor-found} lays out the theoretical foundations for
  project development,
  namely the project development methodologies and associated tools, and the
  communications technologies.
\item In Chapter~\ref{ch:requirements-specs} are identified the key requirements
  and constraints the system being developed must meet from the end-user
  perspective (requirements) and, by defining well-established boundaries within
  the project resources (time, budget, technologies and know-how), the list of
  spefications is obtained.
\item After defining the product specifications, the solutions space is explored
  in Chapter~\ref{ch:analysis}, providing the rationale for viable solutions and
  guiding the designer towards a best-compromise solution, yielding the
  preliminary design and the foreseen tests to the specifications.
\item The preliminary design is further refined in Chapter~\ref{ch:design} and
  decomposed into tractable blocks (subsystems) which can be designed
  independently and assigned to different design teams, allowing the transition
  to the implementation phase.
\item Next, in Chapter~\ref{ch:implementation}, the design solution is
  implemented into the target platforms.
\item Then, in Chapter~\ref{ch:testing}, the implementation is tested at the
  subsystem level (unit testing) and system level (integrated testing),
  analysing and comparing the attained performance with the expected one.
\item After product testing, in Chapter~\ref{ch:verif-valid}, the specifications
  must be verified and validated by an external agent.
  subsystem level (unit testing) and system level (integrated testing),
  analysing and comparing the attained performance with the expected one.
\item Chapter~\ref{ch:conclusion} gives a summary of this report as well as
  prospect for future work.
\item Lastly, the appendices (see Section~\ref{ch:Append}) contain detailed
  information about project planning and development.
\end{itemize}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../../dissertation"
%%% End:
